Article title

### 2017-08-03 paper-webserver.tex
ADD: something looking like a 2nd para

% 1. Our specific problem, previous work
We have previously developed Superphy \cite{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.
Superphy integrates pre-computed results with domain-specific metadata to provide real-time analyses of epidemiology relations over thousands of genomes.
To scale Superphy for tens of thousands of genomes and for use by front-line clinicians, software pipelines should run in real-time and existing population-wide analyses should automatically integrate new results.

@@

% potential of WGS
, and as such can be used to evaluate the spread of outbreaks with better resolution and context than traditional methods \cite{ronholm2016navigating}.
However, while these WGS-based methods can fully examine the underlying genetics, the expressed phenotype is more difficult to predict.
For example, predictions involving reference databases are only as good as the databases themselves.
Additionally, the cost of developing, approving, and transforming existing workflows from wet-lab to sequence prediction approaches in time consuming and expensive \cite{koser2012routine}.

@@

% Superphy
, which provided pre-computed, predictive genomic analyses for determining Shiga toxin subtype, AMR gene profiles, the presence of known virulence factors, and provides predictive biomarkers, both the presence / absence of genomic regions and single nucleotide variants, for bacterial sub-groups based on metadata such as serotype, host source, or location.
While this tool has been useful for the thousands of pre-computed genomes in its database, the current pace of genome sequencing requires real-time predictive genomic analyses of tens of thousands of genomes, and the long term storage and referencing of these results, something that the original SuperPhy platform was incapable of.

In this study, we present an update to the SuperPhy platform, called Spfy.
It is backed by a graph database and takes a modular approach to tool integration and distributes analyses over task queues, thereby allowing modules to run in parallel in real-time, and address code failures.
This allows large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistically significance testing of genome markers for user-defined groups.
Lastly, these services are containerized using Docker to mitigate the complexities of the underlying bioinformatic pipelines.
All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

>>>>

% 1. Our specific problem, previous work
We have previously developed Superphy \cite{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.
Superphy integrates pre-computed results with domain-specific metadata to provide real-time analyses of epidemiology relations over thousands of genomes.
While this tool has been useful for the thousands of pre-computed genomes in its database, the current pace of genome sequencing requires real-time predictive genomic analyses of tens of thousands of genomes, and the long term storage and referencing of these results, something that the original SuperPhy platform was incapable of.
% 2. Why solving it is important (for Public health / research)
WGS offers better resolution than traditional strain comparison methods, such as  pulsed-field gel electrophoresis (PFGE) \cite{ronholm2016navigating}, and is set to replace the functions of reference laboratories.
Though the cost of developing, approving, and transforming existing workflows from wet-lab to sequence prediction approaches in time consuming and expensive \cite{koser2012routine}, performing real-time analyses and linkage to thousands of historical results is only possible through WGS.
% 3. how we solved it
In this study, we present an update to the SuperPhy platform, called Spfy.
Our update rewrites result storage with backing by a graph database and takes a modular approach to tool integration and distributes analyses over task queues, thereby allowing users to submit genomes and modules to run in parallel in real-time, and address code failures.
All results are stored as a series of linked nodes which enables the platform to build associations between results as they are generated. \par

% 4. benefits: rapid analyses in real-time -> huge comparisons, replace reference labs -> time & money saved, future work -> expand analyses, more genomes, more species
This allows large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistical significance testing of genome markers for user-defined groups.

@@

% potential of WGS
, and as such can be used to evaluate the spread of outbreaks with better resolution and context than traditional methods \cite{ronholm2016navigating}.
However, while these WGS-based methods can fully examine the underlying genetics, the expressed phenotype is more difficult to predict.
For example, predictions involving reference databases are only as good as the databases themselves.

@@

% Superphy
, which provided pre-computed, predictive genomic analyses for determining Shiga toxin subtype, AMR gene profiles, the presence of known virulence factors, and provides predictive biomarkers, both the presence / absence of genomic regions and single nucleotide variants, for bacterial sub-groups based on metadata such as serotype, host source, or location.

Lastly, these services are containerized using Docker to mitigate the complexities of the underlying bioinformatic pipelines.
All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.
